Crystal as a thermodynamic computer

### 2024-09-14 paper/main.tex
update

Assume the SA procedure in each block has an error probability $\epsilon$.
Repeating the procedure in $\frac{M}{W}$ blocks results in a success probability of $(1 - \epsilon)^{\frac{M}{W}}$ for finding the global ground state. 
To fix the success probability for arbitrary $M$, we must have $\epsilon \sim \frac{W}{M}$.
The annealing time $t_{th}$ required to achieve a certain error in each block is determined by the spectral gap $\Delta$ of the Markov transition matrix of the SA update on the block.
%Since the largest eigenvalue of a transition matrix is 1, the spectral gap is $\Delta = 1 - \lambda_2$, where $\lambda_2$ is the second-largest eigenvalue.
The scaling behavior of $\Delta$ and block size $W$ can be complicated, in the worst case, it can be exponential, i.e.,
\begin{equation}
    \label{eq:spectral-gap}
    \Delta \sim e^{-W}.
\end{equation}
Consequently, $t_{th}$ is related to $\epsilon$ by $\left( 1-\Delta \right) ^ {t_{th}} = \epsilon$, which gives $t_{th} \sim \ln(\frac{M}{W})e^{W}$, and the total sweep times scale as $\frac{M}{W}\ln(\frac{M}{W})e^W$.

@@

We can define an effective heat zone with width $W'$ as the width of the raising edge of the temperature distribution, where the spins can be cooled actively.
%Defining $\Delta E_{max}$ to be the largest possible energy change when a spin is fliped.
%The effective heat zone with width $W'(\Lambda)$ should then be $[y-W'(\Lambda), y]$, where position $y$ satisfying 
%$\exp(\frac{\Delta E_{max}}{T(y)}) = 0.1$ and $y<L(t)$. 
% Since the layers in fronts of the effective heat zone can only be fliped with a $\epsilon$ probability if the local energy would increase. 
The spins outside the effective heat zone are either frozen (too cold) or flip randomly (too hot).
As a spin flips with a probability $\sim e^{-\Delta E/T}$, the cold edge of the heat zone can be defined as the position where the probability of flipping is $\epsilon$.
We have $W'$ scales with the required error probability $\epsilon$ as:
\begin{equation}
    e^{-\frac{\Delta E}{T_{\rm max}}\Lambda^{cW'}} \sim \epsilon
\end{equation}
where $c$ is an empirical constant and can be determined during the experiment. 
\ym{I am not sure about how to give a concrete definition of the effective width $W'$.}\jinguo{How about this?}

The total sweep time with a fixed inputs size $N$ can then be calculated as

\begin{equation}
    \label{eq:total-annealing-time}
    t_{total} \propto \frac{M}{W'}(\ln(\frac{M}{W'}))^{1+ \frac{1}{c\ln(\Lambda)}}
\end{equation}

@@

\begin{figure*}[]
    \centering
    \vspace*{-\topskip}
    \includegraphics[width=\textwidth,keepaspectratio]{../notes/images/main_result.pdf}
    \caption{Numerical Result.
    \jinguo{images should use the pdf format, the font size should be larger. Is it possible to verify that the Ising model is similar to the toy model? What is $T$ in the xlabel?}
    \ym{If a comparison between Ising model and toy model is a must, plese inform me.}
    }
    \label{fig:main-numerical-result}
\end{figure*}

>>>>

Assume the SA procedure in each block has an error probability $\epsilon$.
Repeating the procedure in $\frac{M}{W}$ blocks results in a success probability of $(1 - \epsilon)^{\frac{M}{W}}$ for finding the global ground state. 
To fix the success probability for arbitrary $M$, we must have $\epsilon \sim \frac{W}{M}$.
The annealing time $t_{th}$ required to achieve a certain error in each block is determined by the spectral gap $\Delta$ of the Markov transition matrix of the SA update on the block.
%Since the largest eigenvalue of a transition matrix is 1, the spectral gap is $\Delta = 1 - \lambda_2$, where $\lambda_2$ is the second-largest eigenvalue.
The scaling behavior of $\Delta$ and block size $W$ can be complicated, in the worst case, it can be exponential, i.e.,
\begin{equation}
    \label{eq:spectral-gap}
    \Delta \sim e^{-W}.
\end{equation}
Consequently, $t_{th}$ is related to $\epsilon$ by $\left( 1-\Delta \right) ^ {t_{th}} = \epsilon$, which gives $t_{th} \sim \ln\left(\frac{M}{W}\right)e^{W}$, and the total sweep times scale as:
\begin{equation}\label{eq:totaltime}
t_{\rm total} \sim \frac{M}{W}\ln\left(\frac{M}{W}\right)e^W.
\end{equation}

@@

We can define an effective heat zone with width $W'$ as the width of the raising edge of the temperature distribution, where the spins can be cooled actively.
%Defining $\Delta E_{max}$ to be the largest possible energy change when a spin is fliped.
%The effective heat zone with width $W'(\Lambda)$ should then be $[y-W'(\Lambda), y]$, where position $y$ satisfying 
%$\exp(\frac{\Delta E_{max}}{T(y)}) = 0.1$ and $y<L(t)$. 
% Since the layers in fronts of the effective heat zone can only be fliped with a $\epsilon$ probability if the local energy would increase. 
The spins outside the effective heat zone are either frozen (too cold) or flip randomly (too hot).
As a spin flips with a probability $\sim e^{-\Delta E/T}$, the cold edge of the heat zone can be defined as the position where the probability of flipping is $\epsilon$.
We have $W'$ scales with the required error probability $\epsilon$ as:
\begin{equation}
    e^{-\frac{\Delta E}{T_{\rm max}}\Lambda^{cW'}} \sim \epsilon
\end{equation}
where $c$ is an empirical constant and can be determined during the experiment. 
\ym{I am not sure about how to give a concrete definition of the effective width $W'$.}\jinguo{How about this?}
We have $\log(\Lambda) cW' \sim \log(\frac{T_{\rm max}}{\Delta E}\log(\frac{1}{\epsilon}))$.

Combining with \Cref{eq:totaltime}, the total annealing time can be estimated as
\begin{equation}
    \label{eq:total-annealing-time}
    t_{\rm total} \sim \frac{M}{W'}\left(\ln\left(\frac{M}{W'}\right)\right)^{1+ \frac{1}{c\ln(\Lambda)}}
\end{equation}

@@

\begin{figure*}[]
    \centering
    \vspace*{-\topskip}
    \includegraphics[width=\textwidth,keepaspectratio]{../notes/images/main_result.pdf}
    \caption{Numerical Result.
    \jinguo{images should use the pdf format, the font size should be larger. Is it possible to verify that the Ising model is similar to the toy model? What is $T$ in the xlabel?}
    \ym{If a comparison between Ising model and toy model is a must, plese inform me.}
    \jinguo{(1) We should make the lines in (c) fit better with the data points. (2) Please complete the caption. You need to at least explain the short notations: GA, HB. (3) Please use log-scale axes for (a) and (c), instead of taking log directly on the data points. $\ln(\ln(M))$ is difficult to interpret.}
    }
    \label{fig:main-numerical-result}
\end{figure*}
